%-------------------------
% Resume in LaTeX
% Author : Avni Sanghvi
% License : MIT
%------------------------


\documentclass[letterpaper,11pt]{article}
\usepackage{enumitem}
\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}
\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure PDF is machine-readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{\item\small{#1\vspace{-2pt}}}
\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
  \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
    \textbf{#1} & #2 \\
    \textit{\small#3} & \textit{\small #4} \\
  \end{tabular*}\vspace{-7pt}
}
\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}[leftmargin=0.15in]}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

%----------HEADING----------
\begin{center}
    \textbf{\Huge \scshape Avni Sanghvi} \\ \vspace{1pt}
    \small +1 312-774-0767 $|$ \href{mailto:avnikhandhar.us@gmail.com}{\underline{avnikhandhar.us@gmail.com}} $|$
    \href{https://www.linkedin.com/in/avnisanghvi}{\underline{linkedin.com/in/avnisanghvi}} $|$
    \href{https://public.tableau.com/app/profile/avni.sanghvi/vizzes}{\underline{Tableau Portfolio}}
\end{center}

%-----------EXPERIENCE-----------
\section{Experience}
\resumeSubHeadingListStart
  \resumeSubheading
    {Senior Database Administrator}{Mar 2021 – Feb 2025}
    {Wipro Technologies}{Mumbai, India}
    \resumeItemListStart
      \resumeItem{Led end-to-end administration of Oracle NoSQL Database (v23.1) in a high-availability, 24x7 production environment, achieving 99.9\% uptime across multiple enterprise clients.}
      \resumeItem{Troubleshot and resolved complex performance bottlenecks and system outages, reducing incident resolution time by 25\% and improving mean time to recovery (MTTR).}
      \resumeItem{Optimized database queries and indexing strategies, boosting query performance by 30\% and cutting down manual reporting effort by 40\%.}
      \resumeItem{Streamlined database operations by scripting administrative tasks using Linux CLI and automating daily health checks, improving operational efficiency.}
      \resumeItem{Designed and implemented robust backup, recovery, and replication strategies ensuring data integrity and disaster recovery readiness.}
      \resumeItem{Integrated and managed ELK Stack (Elasticsearch, Logstash, Kibana) to monitor cluster health, enabling real-time diagnostics and accelerating issue resolution.}
      \resumeItem{Led proactive storage forecasting and capacity planning, reducing unplanned outages by 20\% and ensuring optimal resource utilization.}
      \resumeItem{Collaborated with cross-functional teams including application developers, QA, and DevOps to align database strategies with project goals and deployment pipelines.}
      \resumeItem{Mentored junior DBAs and created documentation for best practices in NoSQL database tuning, contributing to team scalability and knowledge retention.}
    \resumeItemListEnd
\resumeSubHeadingListEnd

%-----------EDUCATION-----------
\section{Education}
\resumeSubHeadingListStart
  \resumeSubheading
    {Chhattisgarh Swami Vivekanand Technical University}{June 2020}
    {Bachelor of Technology in Computer Science -- 8.89/10}{Bhilai, India}
  \resumeSubheading
    {Holy Hearts Educational Academy}{April 2016}
    {Higher Secondary Certificate -- 75\%}{Raipur, India}
  \resumeSubheading
    {Holy Hearts Educational Academy}{April 2014}
    {Secondary School Certificate -- 9.4/10}{Raipur, India}
\resumeSubHeadingListEnd

%-----------CERTIFICATIONS-----------
\section{Certification}
\resumeSubHeadingListStart
  \resumeSubheading
    {Machine Learning Program (Certificate Course)}{May 2024}
    {National Institute of Information Technology}{India}
    \resumeItemListStart
      \resumeItem{Developed a strong foundation in \textbf{data pre-processing}, cleaning, and transformation, emphasizing real-world data integrity.}
      \resumeItem{Utilized \textbf{MS Excel} for advanced data analysis and visualization.}
      \resumeItem{Applied \textbf{SQL} for efficient querying and manipulation of relational data.}
      \resumeItem{Gained proficiency in \textbf{Python for Data Science} with libraries such as Pandas, NumPy, Matplotlib, and Seaborn.}
      \resumeItem{Built dashboards using \textbf{Tableau} to tell compelling stories through data.}
      \resumeItem{Engineered and tested \textbf{machine learning models} (classification, regression) using scikit-learn.}
      \resumeItem{Completed a \textbf{capstone project} simulating full-cycle data science workflow from analysis to deployment.}
    \resumeItemListEnd
\resumeSubHeadingListEnd

%-----------ACCOMPLISHMENTS-----------
\section{Accomplishments}
  \resumeItemListStart
    \resumeItem{State-level (West Bengal, India) Runner-up in UCMAS, Abacus.}
    \resumeItem{National-level (India) Consolation Prize holder in UCMAS, Abacus.}
  \resumeItemListEnd


%-----------PROJECTS-----------
\section{Projects}
\resumeSubHeadingListStart

  \resumeSubheading
    {IMDB Data Analysis}{}{Python, MS Office, Tableau}{}
    \resumeItemListStart
      \resumeItem{Built classification models to predict movie revenue, genre, and ratings using preprocessed JSON data.}
    \resumeItemListEnd
  \vspace{4pt}

  \resumeSubheading
    {Automobile Data Set Analysis}{}{Python, MS Excel, Tableau, Figma}{}
    \resumeItemListStart
      \resumeItem{Analyzed product sales trends across regions and categories to identify business insights.}
    \resumeItemListEnd
  \vspace{4pt}

  \resumeSubheading
    {Movie Rental Data Analysis}{}{MySQL, MS Office}{}
    \resumeItemListStart
      \resumeItem{Explored rental patterns to determine top-performing genres, customers, and actors.}
    \resumeItemListEnd
  \vspace{4pt}

  \resumeSubheading
    {TMDB Movie Data Analysis}{}{Python, MS Office}{}
    \resumeItemListStart
      \resumeItem{Performed EDA to understand the factors contributing to movie success and audience engagement.}
    \resumeItemListEnd
  \vspace{4pt}

  \resumeSubheading
    {Customer Churn Analysis}{}{Tableau, MS Office}{}
    \resumeItemListStart
      \resumeItem{Created dashboards to analyze churn drivers and inform a 10\% churn reduction strategy.}
    \resumeItemListEnd
  \vspace{4pt}

  \resumeSubheading
    {Prediction of Insurance Premium}{}{Python for ML, MS Office}{}
    \resumeItemListStart
      \resumeItem{Developed regression models to forecast premium costs and improve risk pricing.}
    \resumeItemListEnd
  \vspace{4pt}

  \resumeSubheading
    {Prediction of Customer Churn in Banking}{}{Python for ML, MS Office}{}
    \resumeItemListStart
      \resumeItem{Implemented classification algorithms to identify customers at risk of churn.}
    \resumeItemListEnd
  \vspace{4pt}

  \resumeSubheading
    {Prediction of Absenteeism in Employees}{}{Python for ML, MS Office}{}
    \resumeItemListStart
      \resumeItem{Built models to classify and cluster absenteeism patterns for HR policy refinement.}
    \resumeItemListEnd

\resumeSubHeadingListEnd



%-----------TECHNICAL SKILLS-----------
\section{Technical Skills}
\resumeSubHeadingListStart
  \item{
    \textbf{Languages}{: Python, Java, C, C++} \\
    \textbf{Tools}{: MS Office, Tableau, SQL, Oracle NoSQL} \\
    \textbf{Operating Systems}{: Windows, Linux}
  }
\resumeSubHeadingListEnd


\end{document}
